\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Engineer}
    {8fit}
    {Germany/Berlin}
    {Aug. 2018 - Present}
    {
      \begin{cvitems}
        \item {Ownership of backend platform and API.}
        \item {Establishing quality assurance control measures.}
        \item {Establishing development standards like single style and documentation.}
        \item {Coaching data engineering team on Python specific topics.}
        \item {Planning and excution of technical challenges.}
        \item {Responsible for taking decisions, refining solutions and conduction RnD before team starts any activity.}
        \item {Delivering campaign and promotion platform built using Gatsby, GraphQL and Django.}
        \item {Continuous Delivery and CI automation.}
      \end{cvitems}
    }
  \cventry
    {Backend developer}
    {ADAC Camping}
    {Germany/Berlin}
    {Mar. 2018 - Jul. 2018}
    {
      \begin{cvitems}
        \item {Actively practicing lean scrum and agile methodologies.}
        \item {Ownership of multiple microservices.}
        \item {Coaching and supporting frontend developers on technical challenges.}
        \item {Leading backend development for new camping platform.}
        \item {Planning features and implementing solutions.}
        \item {Continuous Delivery and CI automation using CircleCI and Docker containers.}
        \item {Supporting frontend, product and management teams.}
      \end{cvitems}
    }
  \cventry
    {Python engineer}
    {CeleraOne GmbH}
    {Germany/Berlin}
    {Jul. 2016 - Mar. 2018}
    {
      \begin{cvitems}
        \item {Developing biggest European paid content system.}
        \item {Developing paywall solutions from concept stage to integration stages.}
        \item {Working on backend systems and API based on Python \& Pyramid.}
        \item {Supporting Machine Learning team on Python stack.}
        \item {Ownership of metric aggregation platform.}
        \item {Developing new metrics required to reflect business goals and expectations.}
        \item {Business Intelligence Metrics aggregation using distributed scheduling on Celery.}
      \end{cvitems}
    }
  \cventry
    {Senior Python engineer \& Full stack developer}
    {Dmetrics \& Zensoft}
    {Kyrgyzstan/Bishkek}
    {Oct. 2015 - Jul. 2016}
    {
      \begin{cvitems}
        \item {Coaching front-end teams and helping on making decisions on front-end stack.}
        \item {Working on backend systems and API based on Python \& Django.}
      \end{cvitems}
    }
  \cventry
    {Freelance projects}
    {Spalmalo.com - http://spalmalo.com.}
    {Kyrgyzstan/Bishkek}
    {2014 - 2015}
    {
      \begin{cvitems}
        \item {Online FM Radio application NeFm and radio station aggregator mob.fm (Android)}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Namba Media \& BeSmart}
    {Kyrgyzstan/Bishkek}
    {Q2 2013}
    {
      \begin{cvitems}
        \item {Lead developer at Groupon like company in post USSR countries http://besmart.kg}
        \item {Performance optimisation for backend systems, report generation performance tuning.}
        \item {Full-stack development at Social media company http://namba.kg}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Tivix inc.}
    {California/Palo Alto}
    {Mar. 2012 - Dec. 2012}
    {
      \begin{cvitems}
        \item {Development a PoC for debating platform based Django/Python and TokBox.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
  \cventry
    {Consulting projects}
    {Signle Window State Enterprise Customs Service}
    {Kyrgyzstan/Bishkek}
    {Apr. 2011 - Oct. 2011}
    {
      \begin{cvitems}
        \item {RnD and Business solutions developer, Signle Window State Enterprise for Kyrgyz Customs http://swis.trade.kg/}
      \end{cvitems}
    }

  \cventry
    {Web developer \& Project manager}
    {CIIP (Civil Initiative on Internet Policy Public foundation)}
    {Kyrgyzstan/Bishkek}
    {Jun. 2007 - Jan. 2012}
    {
      \begin{cvitems}
        \item {Development and maintaining internal office projects}
        \item {Management of localisation project to translate Gnome 2 and Open office to Kyrgyz language.}
      \end{cvitems}
    }
\end{cventries}
